---
title: "Raudio"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Raudio}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
# library(roeis)
```

# Objective

The purpose of this vignettes is to explain how the audio package can be used to play sounds from integers. We start by loading the package\

```{r, warning=FALSE}
library(audio)
```

# The Audio Package

The audio package was designed to interface to audio devices, such as Windows MM or Mac OS, to allow users to record and playback audio. In this vignette we will only refer to some of the functions included in this package, specifically those that create new audio instances. Readers interested in a complete description of the audio package capabilities should look into the [rforge website](http://www.rforge.net/audio/).

# Creating Audio Objects

To create audio objects from a series of integers we will use the function `audioSample()`. This is a constructor that takes in numeric vectors or matrices, marks them with audio information and returns objects of the S3 class `audioSample`. As we will see later on, there are S3 methods to play audio from objects of this class.\

The `audioSample()` function has 4 arguments:\

* `x`: the numeric vector or matrix that will be used to generate the digitalized audio data. If a vector, then only one channel will be used; if a matrix, then R will set as many channels as rows in the matrix.\

* `rate`: the number of samples taken per second to generate the digital audio file.  As a reference, CDs are usually recorded at 44.1 Hz, which means 44.1 samples are taken every second. Since the length of `x` will define the number of samples, and `rate` will determine the number of samples per second, together `x` and `rate` define the duration of the audio created\
