---
title: "Raudio"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Raudio}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
# library(roeis)
```

# Objective

The purpose of this vignettes is to explain how the audio package can be used to play sounds from integers. We start by loading the package\

```{r, warning=FALSE}
library(audio)
```

# The Audio Package

The audio package was designed to interface to audio devices, such as Windows MM or Mac OS, to allow users to record and playback audio. In this vignette we will only refer to some of the functions included in this package, specifically those that create new audio instances. Readers interested in a complete description of the audio package capabilities should look into the [rforge website](http://www.rforge.net/audio/).

# Creating Audio Objects

To create audio objects from a series of integers we will use the function `audioSample()`. This is a constructor that takes in numeric vectors or matrices, marks them with audio information and returns objects of the S3 class `audioSample`. As we will see later on, there are S3 methods to play audio from objects of this class.\

The `audioSample()` function has 4 arguments:\

* `x`: the numeric vector or matrix that will be used to generate the digitalized audio data. If a vector, then only one channel will be used; if a matrix, then R will set as many channels as rows in the matrix.\

* `rate`: the number of samples taken per second to generate the digital audio file.  As a reference, CDs are usually recorded at 44.1 Hz, which means 44.1 samples are taken every second. Since the length of `x` will define the number of samples, and `rate` will determine the number of samples per second, together `x` and `rate` define the duration of the audio created\

* `bits`: the number indicating what the resolution of the audio is. The more bits used, the better the audio quality. 

* `clip`: a logical value. If true, the imputed integers are forced into a range between -1 and 1.\ 

Once we have our audio data, we can reproduce it with `play()`. This is the S3 method for objects of class `AudioSample` and it only takes as input the data to play.\

We will work through an example to illustrate how to create audio sample objects from integers. We start by creating a numeric vector, `sequence1`, that contains the first 10,000 positive integers, each of them divided by 100.\

```{r}
sequence1 <- 1:10000 / 100
```

Now we use `audioSample()` to generate some audio data from our sequence. We set the sample rate to 10000 and the bits to 16. In this case, we won't clip the range of the inputted values. We save the returned object as audio1\

```{r}
audio1 <- audioSample(x = sequence1, rate = 10000, bits = 16, clip = FALSE)
```

**COMMENT ON STRUCTURE?**
```{r}
str(audio1)
```


As expected, `audio1` is an object of class `AudioSample`.\

```{r}
class(audio1)
```

The underlying data type is double, because what we tagged our numeric vector with audio information.\

```{r}
typeof(audio1)
```


It is worth pointing out that there are methods defined for this class of object that allow the user to check and set the attributes.\

For example:
```{r}
# Checking bits
audio1$bit

# Checking rate
audio1$rate
```

We can now play the audio. Pay attention to the pitch and the duration.

```{r}
play(audio1)
```

As we indicated before, the length of the imputed vector determines the number of samples  used to create the audio. So if `x` was twice as long, we should have and audio that is twice as long as `audio1`.\

We can test this. Let's create a second audio sample using the same arguments for everything but argument `x`. This time we will use a larger object. Our original sequence had 10,000 values, so let's change it to 20,000. Since the rate (number of samples taken per second) remains the same, the audio should last longer.\ 
```{r}
# Creating new audio sample
audio2 <- audioSample(rep(sequence1,2), 10000, bits = 16, clip =FALSE)

# Playing audio
play(audio2)
```
