---
title: "Rcache"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Rcache}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
# library(roeis)
```

## Objective
As dictated in the [CRAN Repository Policy](https://cran.r-project.org/web/packages/policies.html), data used in CRAN packages should not surpass 5MB. The Online Encyclopedia of Integer Sequences (OEIS) database used in the `roeis` package is approximately 71MB when originally downlaoded and when compressed, approximately 28MB. Therefore, it is necessary to explore other options for loading and storing data in the `roeis` package. Caching and memoization provide an efficient means of avoiding having to run large, repetitive, and time-consuming code. 

This vignette aims to explore caching and memoization via the `R.cache` package.

## What Are Caching and Memoization?

## `R.cache` Package
### Overview
[R.cache CRAN documentation](https://cran.r-project.org/web/packages/R.cache/index.html)

### Key Functions

## Examples
### Download Data

### Implement Cached Data

## Exercise
