---
title: "Rcache"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Rcache}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
# library(roeis)
```

## Objective
As dictated in the [CRAN Repository Policy](https://cran.r-project.org/web/packages/policies.html), data used in CRAN packages should not surpass 5MB. The Online Encyclopedia of Integer Sequences (OEIS) database used in the `roeis` package is approximately 71MB when originally downlaoded and when compressed, approximately 28MB. Therefore, it is necessary to explore other options for loading and storing data in the `roeis` package. Caching and memoization provide an efficient means of avoiding having to run large, repetitive, and time-consuming code. 

This vignette aims to explore caching and memoization via the `R.cache` package.

## What Are Caching and Memoization?

## `R.cache` Package
Let's load the `R.cache` library.
```{r}
library(R.cache)
```


### Overview
[R.cache CRAN documentation](https://cran.r-project.org/web/packages/R.cache/index.html)

### Key Functions
`R.cache` contains seven functions:

* `addMemoization()`
* `evalWithMemoization()`
* `getCacheRootPath()`
* `loadCache()`
* `memoizedCall()`
* `saveCache()`
* `setCacheRootPath()`

For the purpose of this project, the two functions we will explore are `saveCache()` and `loadCache()`.

## Examples
Let's take a look a some real-world data. Beginning January 21, 2020, The New York Times (NYT) has collected data on COVID cases in the United States and across the world. Current coverage of the pandemic can be viewed [on the NYT website](https://www.nytimes.com/interactive/2021/us/covid-cases.html) and live updates of their datasets can be accessed via their [COVID 19 Data Github Repo](https://github.com/nytimes/covid-19-data). 

In order to practice loading in a dataset that is larger than 5MB and caching it, we will use the `us-counties-2022.csv` that can be accessed [here](https://github.com/nytimes/covid-19-data/blob/master/rolling-averages/us-counties-2022.csv).

### Download Data via `saveCache()`
```{r}
# key <- read.csv("~/us-counties-2022.csv")
# 
# what <- loadCache(key)
# what
# class(what)
# typeof(what)
```


### Load Cached Data via `loadCache()`
```{r}
# loadCache(what)
```


## Exercise
